The Lipid Interactome Repository

### 2025-02-25 IndividualStudies/RM_2021.qmd
new links on index.qmd, reduced library redundancy

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(htmltools)
library(here)

>>>>

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

### 2025-02-25 IndividualStudies/SF_2024.qmd
new links on index.qmd, reduced library redundancy

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(htmltools)
library(scales)
library(here)

>>>>

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

### 2025-02-25 IndividualStudies/SF_2024_B.qmd
new links on index.qmd, reduced library redundancy

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(here)

>>>>

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

### 2025-02-25 LipidProbe/1-10_FattyAcid.qmd
new links on index.qmd, reduced library redundancy

<!-- R setup, reading dataframes and minor data wrangling -->
```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(htmltools)
library(here)

>>>>

<!-- R setup, reading dataframes and minor data wrangling -->
```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

### 2025-02-25 LipidProbe/Sphinganine.qmd
new links on index.qmd, reduced library redundancy

```{r setup, echo=FALSE, warning=FALSE, include = FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(here)

>>>>

```{r setup, echo=FALSE, warning=FALSE, include = FALSE}
## intitialize libraries
library(here)

### 2025-02-25 index.qmd
new links on index.qmd, reduced library redundancy

@@

>>>>

## Need more info?

@@

See our [Proteomics Methodology Overview](/Background/ProteomicsUsingMultifunctionalProbes.qmd) for more details about the quantification methods used in the data presented in this repository.

See our [Data Analysis Overview](/Background/DataAnalysisAndStatistics.qmd) for more details about the data analysis between the raw mass spectrometry data and the final data presented here.
